Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-11-11 Paper/ms.tex
Another Feroz reference

\subsection{Inferring the number of planets}
The number of orbiting planets, $N$, is an important parameter.
To calculate the posterior distribution for $N$, most authors
consider various trial values of $N$, and calculate the marginal likelihood
\begin{eqnarray}
p(\bdata | N) &=& \int p(\btheta | N) p(\bdata | \btheta, N) \, d^n \btheta
\end{eqnarray}
for each possible value of $N$
\citep[e.g.][]{2011MNRAS.415.2523G, 2014MNRAS.437.3540F, fengji}, marginalising
over all other model parameters.
The posterior distribution for $N$ can then be found straightforwardly by
using Bayes' rule with $N$ as the only unknown parameter:
\begin{eqnarray}
p(N | \bdata) &=& \frac{p(N)p(\bdata | N)}{\sum_N p(N)p(\bdata | N)}.
\end{eqnarray}
Popular
methods for calculating the marginal likelihood are Nested Sampling
\citep{skilling} and ideas related to thermodynamic integration
\citep[e.g.][]{neal}.

@@

>>>>

\subsection{Inferring the number of planets}
The number of orbiting planets, $N$, is an important parameter.
To calculate the posterior distribution for $N$, most authors
consider various trial values of $N$, and calculate the marginal likelihood
\begin{eqnarray}
p(\bdata | N) &=& \int p(\btheta | N) p(\bdata | \btheta, N) \, d^n \btheta
\end{eqnarray}
for each possible value of $N$
\citep[e.g.][]{2011MNRAS.415.2523G, 2011MNRAS.415.3462F, 2014MNRAS.437.3540F, fengji}, marginalising
over all other model parameters.
The posterior distribution for $N$ can then be found straightforwardly by
using Bayes' rule with $N$ as the only unknown parameter:
\begin{eqnarray}
p(N | \bdata) &=& \frac{p(N)p(\bdata | N)}{\sum_N p(N)p(\bdata | N)}.
\end{eqnarray}
Popular
methods for calculating the marginal likelihood are Nested Sampling
\citep{skilling} and ideas related to thermodynamic integration
\citep[e.g.][]{neal}.

@@

\bibitem[\protect\citeauthoryear{Feroz, Balan, 
\& Hobson}{2011}]{2011MNRAS.415.3462F} Feroz F., Balan S.~T., Hobson M.~P., 2011, MNRAS, 415, 3462
